Selecting and Controlling Physical Devices Through Head-Mounted Infrared Targeting

### 2013-09-13 doc/sigchi14/control.tex
progress with text and figures

\section{Example Scenarios}
\bjoern{Here we should either describe a couple of example scenarios we've built, or get some students to run through realistic control tasks based on those scenarios - e.g.: ``Dim the light to 20\% and then start the movie, turn up the volume to 80\%."}

>>>>

\section{Example SmartHome Scenarios}
To understand how our device could be used to interact with smart appliances, we also asked all study participants to work through a concrete scenario. The main goal was to obtain qualitative feedback on the usability and utility of our device with more realistic tasks.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/smarthome-scenario.jpg}
\caption{In the targeting study, participants had to find and select one of 10 targets in a lab environment.}
\label{fig:smarthome}
\end{figure}

\subsection{Methodology}
We recreated a living room environment that had three (four?) controllable appliances: a fan, a lamp, and two laptops functioning as an audio and video player, respectively (see Figure~\ref{fig:smarthome}). The fan and lamp had binary controls: they could be switched on or off. The laptop had multiple parameterized functions: participants could start, pause, stop, and rewind  video and audio, and adjust volume.

We then asked users to work through the following script:

\small{
\begin{enumerate}
\item Turn off the lights as you want to watch the movie in a darkened room.
\item You feel a little hot in the room, so you turn on the fan
\item You connect to the Smart TV and start playing the movie. 
\item The volume seems too soft to hear over the fan- turn it up a bit. 
\item After a while, you want to take a break to get a snack. Pause the movie. 
\item When you come back, you've forgotten what was said last - rewind by ~30 seconds and restart the movie. 
\item You stop the movie and turn the lights back on.
\item You want to listen to some music.
\item After awhile, you stop the music
you turn off the fan and leave the room.
\end{enumerate}}

\subsection{Qualitative results}

\bjoern{Here we should either describe a couple of example scenarios we've built, or get some students to run through realistic control tasks based on those scenarios - e.g.: ``Dim the light to 20\% and then start the movie, turn up the volume to 80\%."}

### 2013-09-13 doc/sigchi14/device.tex
progress with text and figures

\subsection{Interaction Flow}
{\bf Look:} Users select a target device by looking in its general direction.
Glass periodically sends a device id through its IR emitter analogous to Patel's approach~\cite{patel_2-way_2003}. Target appliances have IR receivers and offer immediate visual feedback by toggling an LED whenever a valid id is received. They also respond by initiating an XBee radio connection and sending their id. This allows the Glass application to show which devices are currently targeted on the display. \sean{Currently the led is implemented but clients don't response with their IDs and display on Glass at this stage. We can add that. But we felt like the users would use led as the primary indicator and not to distract them with frequently changing the content on the screen? }

>>>>

\subsection{Interaction Flow}
{\bf Look:} Users select a target device by looking in its general direction.
Glass periodically sends a device id through its IR emitter analogous to Patel's approach~\cite{patel_2-way_2003}. Target appliances have IR receivers and offer immediate visual feedback by toggling a red LED whenever a valid id is received. This enables {\em scanning} the environment with ones gaze to see which devices can be controlled. They also respond by initiating an XBee radio connection and sending their id. This allows the Glass application to show which devices are currently targeted on the display. \sean{Currently the led is implemented but clients don't response with their IDs and display on Glass at this stage. We can add that. But we felt like the users would use led as the primary indicator and not to distract them with frequently changing the content on the screen? }

### 2013-09-13 doc/sigchi14/targeting.tex
progress with text and figures

\section{Target Acquisition Experiment}
\bjoern{text from Google Doc goes here}

>>>>

\section{Target Acquisition Experiment}
To understand the accuracy and performance of head-orientation-based  selection through our device, we carried out a comparative target acquisition study, where participants had to connect to wireless nodes with our technique, and a list selection approach.

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/targeting-study-layout.pdf}
\caption{In the targeting study, participants had to find and select one of 10 targets in a lab environment.}
\label{fig:targeting-study-layout}
\end{figure}

\subsection{Apparatus}
In an indoor environment, 10 wireless nodes are spread across a room at various heights and distances (see Figure~\ref{fig:targeting-study-layout}). The nodes are stand-ins for potential smart appliances and have all relevant functionality for targeting and selection, but do not control any actual appliances. Each node is an embedded wireless system with a microcontroller, IR receiver, a wireless XBee radio, and three status LEDs: an orange LED indicates that the device is the target that should be selected in the current trial; a red LED lights up whenever the device receives an IR signal from Glass; a blue LED shows when participants have successfully connected to a device, and is also used for disambiguation when multiple clients are within IR range (see Figure~\ref{fig:target}). Next to each client device, a paper sheet shows a number and letter combination, which are used for uniquely identifying the devices.

\begin{figure}[b]
\centering
\includegraphics[width=0.8\columnwidth]{figures/study-node.pdf}
\caption{An example node from the targeting study --- we constructed 10 such nodes - each mounted in a box.}
\label{fig:targeting-study-layout}
\end{figure}

\subsection{Methodology}
In our within-subjects design, participants performed 15 target acquisition tasks each with two interaction styles. In the {\em infrared} condition, participants used our IR targeting approach; in the {\em list} condition, participants had to look up a device's letter code and select that letter code from a list displayed on their Glass device. The list was navigated with swipe motions on the Glass touchpad. For each task, participants started at a fixed position in the room. The experimenter called out a number and simultaneously started a timer. Participants then had to find the number on sheets printed and affixed to walls and other surfaces. In the {\em infrared} condition, participants then selected and acquired the target by aiming the infrared beam at the target, and confirmed their selection with a touchpad tap. If more than one target was within range, participants had to either use the disambiguation dialog or reposition themselves. In the {\em list} condition, participants had to read the letter next to the number and then select that letter by browsing a linear list shown in their Glass display. While the list was alphabetized, letter arrangement in the room was not. This design required participants to find the target in the room before starting a list navigation to keep conditions similar to each other.

Afterwards, participants completed a survey that elicited answers to Likert-scale questions as well as open-ended answers about their experience.

\subsection{Participants}
We recruited N participants from our institution. X had never used Glass before.

\subsection{Measures}
The main measure was {\bf target acquisition time}: the time required to identify, select, and connect to a wireless target device. We also elicited {\bf user preference}: which interface users preferred for the task after completing the study.

\subsection{Results}

\subsubsection{Performance data}

\subsubsection{User preference}
X of Y users preferred infrared mode over list mode. As slef-report data can skew to please experimenters, we also asked participants to elucidate why they preferred one interface over the other.

\bjoern{Insert summary of survey data on this point here.}

\subsubsection{Qualitative results}
